Figure 3a

### 2017-11-21 inst/stable_line_expression/stable_line_expression.Rmd
adding additional replicates for stable line exp

#remove Skov exp 1 due to variability in technical replicates
data <- filter(data, `Biological Replicate` != 1 | `Cell line` != "Skov3")

@@

data1 <- data1 %>%
  technicalMeans(., groups) %>%
  dct(., gois1, Actin, groups) %>%
  mutate(GOI = as.character(GOI))

data2 <- data2 %>%
  technicalMeans(., groups) %>%
  dct(., gois2, RNU48, groups) %>%
  mutate(GOI = as.character(GOI))

>>>>

#remove Skov exp 1 due to variability in technical replicates
#data <- filter(data, `Biological Replicate` != 1 | `Cell line` != "Skov3")

@@

data1 <- data1 %>%
  technicalMeans(., groups) %>%
  dct(., gois1, Actin, groups, F) %>%
  mutate(GOI = as.character(GOI))

data2 <- data2 %>%
  technicalMeans(., groups) %>%
  dct(., gois2, RNU48, groups, F) %>%
  mutate(GOI = as.character(GOI))
